Extended Data

### 2021-10-06 doc/manuscript/Dow_Extended_Data.Rmd
create Extended Data Table 3
#75

## table captions
species_table_caption <-"Extended Data Table 1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
mean_growth_parameters_caption = "Extended Data Table 2 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest."
tree_ring_summary_caption =  "Extended Data Table 3 | Summary of tree-ring data and analysis ( including species, n chronologies (= n sites), n positively correlated with April T, n sig.)"

@@

## (PLACEHOLDER FOR `r tree_ring_summary_caption` )

>>>>

## table captions
species_table_caption <-"Extended Data Table 1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
mean_growth_parameters_caption = "Extended Data Table 2 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest."
tree_ring_summary_caption =  "Extended Data Table 3 | Summary of tree-ring data and analysis"

@@

## `r tree_ring_summary_caption`

```{r tree_ring_summary,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
TreeRingResultsSummary <- read.csv("tables_figures/TreeRingResultsSummary.csv",  
                                   col.names = c("", "species","n","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-","+", "-"), 
                                   stringsAsFactors = FALSE, check.names = FALSE)
TreeRingResultsSummary <- TreeRingResultsSummary[c(2:19)]
kable(TreeRingResultsSummary, 
      #caption = tree_ring_summary_caption ,  
      format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" " = 2,  "April" = 2, "May" = 2,"June" = 2,"July" = 2,"Aug" = 2,"April" = 2,"June-July" = 2,"A:JJ" = 2)) %>%
add_header_above(c(" " = 1,  "n sig. correlations in univariate analysis" = 10,"n sig. correlations in multivariate analysis" = 6)) %>%
    #column_spec(3:18, width = ".3cm") %>%
pack_rows("Ring Porous", 1, 16, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
pack_rows("Diffuse Porous", 17, 27, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
row_spec(28, bold = T) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
